### 2019-12-12 defesa/tex/chapter/e3p.tex
wip

Then, by its definition is possible to see that every root of $g$ is also a root of $h$. Conversely, every root $\hat{z}$ of $h$ which is in $\mathbb{S}$--or $|\hat{z}|=1$--is also a root of $g$. Naturally, the angle of a root $\hat{z}$ of $g$ is a root of $\xi$ by Euler's Formula.

It is possible to make another reduction to obtain a degree-$6$ polynomial from $h$ whose roots form a superset of the roots of $g$. As it has been mentioned on this chapter, an ellipse is symmetric with respect to its own axis. This means $\theta$ and $\pi + \theta$ are equivalent angles of rotation for any ellipse, thus $\xi(\theta) = \xi(\pi + \theta)$\footnote{$\xi$ is only defined over $[0, \pi)$, so this equality is not actually valid.}. 
On \autoref{chapter:definitions}, it was stated that the angle of $z$ and $-z$ has the same symmetry with each other as an ellipse's angle of rotation:
\begin{equation*}
angle(-z) = \pi + angle(z).
\end{equation*}
From that, as $g(e^{i\theta})=\xi(\theta)$ for every $\theta \in [0, 2\pi)$, we conclude that $g(-z)=g(z)$. This implies that $h$ is, in fact an even polynomial, or that $h(-z) = h(z)$ is true for every $z\in\mathbb{C}$:
\begin{align}
h(-z) = (-z)^6g(-z) = z^6g(z).
\end{align}
Therefore, all the odd degree coefficients of $h$ are $0$ and we can define the $6$-degree polynomial $f : \mathbb{C} \mapsto \mathbb{C}$ with the substitution $y=z^2$:
\begin{equation}
f(y) = \sum_{k=0}^{6} c_{2k} y^k.
\end{equation}
Then from every root $\hat{y}$ of $f$, two roots of $h$ can be obtained: $\sqrt{\hat{y}}$ and $-\sqrt{\hat{y}}$. As the angle of $-\sqrt{\hat{y}}$ is not between $[0, pi)$ we can ignore it. Note that the the square root of $\hat{y}$ does not need to be calculated, as only the angles are needed and they can be obtained by:
\begin{equation}
angle(\sqrt{z}) = angle(z)/2.
\end{equation}
Finally, using the QR algorithm mentioned on \autoref{chapter:definitions} a $\bigO(n^3)$ algorithm, with $n=6$, can be constructed for E3P.

>>>>

Then, by its definition is possible to see that every root of $g$ is also a root of $h$. Conversely, every root $\hat{z}$ of $h$ which is in $\mathbb{S}$--or $|\hat{z}|=1$--is also a root of $g$. Naturally, the angle of a root $\hat{z}$ of $g$ is a root of $\xi$ by Euler's Formula used in the substitution $z=e^{i\theta}$.

It is possible to make another reduction to obtain a degree-$6$ polynomial from $h$ whose roots form a superset of the roots of $g$. As it has been mentioned on this chapter, an ellipse is symmetric with respect to its own axis. This means that $\theta$ and $\pi + \theta$ are equivalent angles of rotation for any ellipse, thus $\xi(\theta) = \xi(\pi + \theta)$\footnote{The domain of $\xi$ is initially set to be $[0, \pi)$, .}. 
On \autoref{chapter:definitions}, it was stated that the angle of $z$ and $-z$ has the same symmetry with each other as an ellipse's angle of rotation:
\begin{equation*}
angle(-z) = \pi + angle(z).
\end{equation*}
From that, as $g(e^{i\theta})=\xi(\theta)$ for every $\theta \in [0, 2\pi)$, we conclude that $g(-z)=g(z)$. This implies that $h$ is, in fact an even polynomial, or that $h(-z) = h(z)$ is true for every $z\in\mathbb{C}$:
\begin{align}
h(-z) = (-z)^6g(-z) = z^6g(z).
\end{align}
Therefore, all the odd degree coefficients of $h$ are $0$ and we can define the $6$-degree polynomial $f : \mathbb{C} \mapsto \mathbb{C}$ with the substitution $y=z^2$:
\begin{equation}
f(y) = \sum_{k=0}^{6} c_{2k} y^k.
\end{equation}
Then from every root $\hat{y}$ of $f$, two roots of $h$ can be obtained: $\sqrt{\hat{y}}$ and $-\sqrt{\hat{y}}$. As the angle of $-\sqrt{\hat{y}}$ is not between $[0, pi)$ we can ignore it. Note that the the square root of $\hat{y}$ does not need to be calculated, as only the angles are needed and they can be obtained by:
\begin{equation}
angle(\sqrt{z}) = angle(z)/2.
\end{equation}
Finally, using the QR algorithm mentioned on \autoref{chapter:definitions} a $\bigO(n^3)$ algorithm, with $n=6$, can be constructed for E3P.
